\documentclass[11pt,a4paper,sans]{moderncv} % Font sizes: 10, 11, or 12; paper sizes: a4paper, letterpaper, a5paper, legalpaper, executivepaper or landscape; font families: sans or roman

\moderncvstyle{classic} % CV theme - options include: 'casual' (default), 'classic', 'oldstyle' and 'banking'
\moderncvcolor{blue} % CV color - options include: 'blue' (default), 'orange', 'green', 'red', 'purple', 'grey' and 'black'

\usepackage{lipsum}
\usepackage[scale=0.75]{geometry} 
\usepackage{fontawesome}
            
\firstname{Antonis}
\familyname{Skarlatos}

\address{}{}{}
\mobile{(+30) 6982443580}
\email{antonisskarlatosj@gmail.com}
\extrainfo{\href{https://www.linkedin.com/in/antonis-skarlatos-b10348197/}{linkedin}, \href{https://github.com/Hepic}{github}, \href{http://bitbucket.com/Hepic}{bitbucket}}

\begin{document}
\makecvtitle

\section{Education}
    \cventry{2014 - 2018}{Undergraduate Student in Computer Science}{CGPA: 8.43/10}{}{}{
    \begin{itemize}
        \item Department of Informatics and Telecommunications
        \item National and Kapodistrian University of Athens
    \end{itemize}}
    
    \cventry{Undergraduate Thesis}{Relationship between treewidth and important parameters and how NP-complete problems can be solved 
    in polynomial time in graphs with bounded treewidth}{}{}{}{
    \begin{itemize}
        \item Greek pdf: \href{https://pergamos.lib.uoa.gr/uoa/dl/frontend/file/lib/default/data/2814438/theFile}{Undergraduate thesis}
        \item Supervisor: Stavros Kolliopoulos
    \end{itemize}}
    
    \cventry{2018 - 2020 (Expected)}{Graduate Student in Theoretical Computer Science}{current CGPA: 9.25/10}{}{}{
    \begin{itemize}
        \item Department of Informatics and Telecommunications, Department of Mathematics, School of Electrical and Computer Engineering
        \item National and Kapodistrian University of Athens, National Technical University of Athens
    \end{itemize}}
    
    \cventry{Graduate Thesis}{The precedence constrained knapsack problem using mostly primal-dual algorithms}{}{}{}{
    \begin{itemize}
        \item Supervisor: Stavros Kolliopoulos
    \end{itemize}}
    
\section{Work Experience}
    \cventry{Ting}{Open source chat}{}{}{}{
    \begin{itemize}
        \item \href{https://github.com/dionyziz/ting}{Ting} is primarily created for educational purposes. It uses \textsc{django} for the back-end 
        and \textsc{react.js} for the front-end.
    \end{itemize}}
    
    \cventry{Freelancing}{\textsc{Freelance Projects}}{}{}{}{
    \begin{itemize}
        \item Part-time freelance projects in C/C++/Python/PHP.
    \end{itemize}}{}
    
    \cventry{University}{University Projects}{}{}{}{
    \begin{itemize}
        \item University projects related to machine learning and big data. In some of them I used the scikit-learn library in
        Python. Also for some projects I have used the LSH technique for finding the closest items based on a specific metric.
    \end{itemize}}
    
\section{Technical Skills}
    \cvitem{Languages (Preferred)}{C, C++, Python}
    \cvitem{Languages (Used)}{Java, C sharp, PHP, Javascript, HTML, CSS, SQL, Prolog, Haskell, Matlab}
    \cvitem{Skills}{Algorithms, Data structures}
    
\section{Hobbies and Interests}
    \cvitem{Computer Science}{I like a lot anything related to algorithms. I like solving problems (Competitive Programming) from websites like \href{http://codeforces.com/}{codeforces}, \href{https://www.topcoder.com/}{topcoder} and taking part in contests. Some achievements are my qualifications in Round 2 of Facebook Cup 2016, 2017 and 2018.}
    \cvitem{Others}{Music, guitar, football, travelling.}
    
\end{document}



